Ignition of Fuel Beds by Firebrands

### 2022-04-10 manuscript3.tex
Updated species study and literature review

    Figure~\ref{fig:composition_plot} shows the averaged cellulose, hemicellulose, and lignin concentrations for each material according to the samples recorded in the Bioenergy Feedstock Library as shown in Table~\ref{tab:composition}. The marker colors for each material correspond to the calculated 50\% ignition probability for the quiescent tests except for the wheat straw and Douglas-fir bark which are denoted as 800\si{\celsius} to indicate that the 50\% ignition probability was higher than the temperatures tested.  Note that due to scaling inherent to a ternary projection the proportion of the fuels characterized as other causes a shift in the data. For example, the wheat straw and Douglas-fir are estimated to have the same cellulose content but do not lie on the same iso-line of 44\% cellulose. Nonetheless, the relative proportions of each constituent are retained and comparisons may still be made. 
            \includegraphics[width=\figureWidthSet, trim={35cm 0 0 0}, clip]{conference_results_binary.png}
            \caption{Estimated chemical composition of each material tested with the marker color representing the estimated 50\% ignition probability. Note that the materials where flaming ignition did not occur are represented as 800\si{\celsius} to show that the temperature of ignition was not achieved.}
            \label{fig:composition_plot}

@@

    Fortunately, both thermal conductivity and chemical composition are measurable material properties and can be simultaneously considered when studying ignition.In summary, characterizing the flaming ignition propensity of fuels with respect to chemical composition alone will likely not yield satisfactory results. The inclusion of other material properties, such as thermal conductivity, however, may add enough additional knowledge for comprehensive predictions of ignition to be made. Further investigation of the differences in chemical and thermal properties of the materials is necessary to unravel the interactions between thermal and chemical processes and the resulting impact on flaming ignition before knowledge sufficient for a predictive tool that may be used for fire prevention and management may be created
    \cite{MacLean1941}.

>>>>

    Figure~\ref{fig:composition_plot} shows the averaged cellulose, hemicellulose, and lignin concentrations for each material according to the samples recorded in the Bioenergy Feedstock Library as shown in Table~\ref{tab:composition}. The marker colors for each material correspond to the calculated 50\% ignition probability for the quiescent tests except for the wheat straw and Douglas-fir bark which are denoted as 800\si{\celsius} to indicate that the 50\% ignition probability was higher than the temperatures tested.  Note that due to scaling inherent to a ternary projection the proportion of the fuels characterized as other causes a shift in the data. For example, the wheat straw and Douglas-fir are estimated to have the same cellulose content but do not lie on the same iso-line of 44\% cellulose. Nonetheless, the relative proportions of each constituent are retained and comparisons may still be made. 
        \begin{figure}[htpb]
            \centering
            \includegraphics[width=\figureWidthSet, trim={35cm 0 0 0}, clip]{conference_results_binary.png}
            \caption{Estimated chemical composition of each material tested with the marker color representing the estimated 50\% ignition probability. Note that the materials where flaming ignition did not occur are represented as 800\si{\celsius} to show that the temperature of ignition was not achieved.}
            \label{fig:composition_plot}
        \end{figure}

@@

    The 50\% ignition probability results for the 5.8\si{\meter\per\second} wind speed tests are shown in Table~\ref{tab:composition50temp} along with the results for the 0.1\si{\meter\per\second} tests. From these results there are three observations of note. First, the increase of wind lowered the threshold for ignition probability for the Douglas-fir wood and Pine wood by approximately 30\%. Second, in contrast to the Douglas-fir and Pine wood results, an increase in wind resulted in a decrease in a higher threshold for ignition.  Third, the materials that were not observed to ignite in the quiescent tests were also not observed to ignite in the presence of wind.

    \begin{table*}[hpbt]
        \caption{Heater temperature required for 50\% probability of ignition for the materials and conditions tested.}
        \centering
        \begin{tabular}{crrr}
            % \rowcolor{gray!50}
            Material & 0.1 \si{\meter\per\second}(\si{\celsius}) & 5.8 \si{\meter\per\second} (\si{\celsius}) & $\Delta$T (\si{\celsius})\\
            \hline
            Douglas-fir Wood & 574  & 391 & -185 \\
            Pine Wood        & 634  & 430 & -204\\
            Oak Wood         & 663  & \textgreater750 & 87\\
            Wheat Straw      & \textgreater750 & \textgreater750 & -\\
            Pine Bark        & \textgreater750 & \textgreater750 & -\\
            Douglas-Fir Bark & \textgreater750 & \textgreater750 & -
        \end{tabular}
        \label{tab:composition50temp}
    \end{table*}

    In summary, characterizing the flaming ignition propensity of fuels with respect to chemical composition alone will likely not yield satisfactory results. The inclusion of other material properties, such as thermal conductivity, however, may add enough additional knowledge for comprehensive predictions of ignition to be made. Further investigation of the differences in chemical and thermal properties of the materials is necessary to unravel the interactions between thermal and chemical processes and the resulting impact on flaming ignition before knowledge sufficient for a predictive tool that may be used for fire prevention and management may be created
    \cite{MacLean1941}.
